A Massive Molecular Gas Reservoir in the $z$ = 2.221 Type-2 Active Galactic Nucleus Host Galaxy SMM J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-06-29 skeleton.tex
before today's correction, going to stick with IR L derived properties

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the lensing FR-II galaxy 3C220.3}
\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
\affil{Astronomy Department, Cornell Unviersity}
\altaffiltext{1}{tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
  of the observable properties of SMGs (cite). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1-3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite). \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently
the brightest known lensed
SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceivable evidence of AGN activity in this SMG, as well as the identification of a type-2 quasar.

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy.

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
\rarr 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam\pmOne.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
%MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne.
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross on each image indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) (H14). The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: \CO line emission}
We detect \CO line emission toward the background SMG SMM J0939. Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission. Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 541.65 $\pm$ 31.91 km s\pmOne. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the \CO detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$378.1 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter.

@@

We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
values of the best-fit lens model \citet{Haas14} performed on Keck K-band near-infrared image. For each of
these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
walkers and 6000 steps to identify the best-fit model parameters.
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit0771}
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
show the negative residuals. \label{fig:lens}}
\end{figure}

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun\ 
and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

@@

The resulting fit is shown in Figure \ref{fig:SED}, the extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement. The 10$\sigma$ detection of the continuum thereby suggests
non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
emission. Furthermore, the contours of the 104 GHz continuum are
centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument. This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah. At the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.

@@

\subsubsection{SMM J0939+8315} 
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting on the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where $T$ is the rest-frame characteristic cold dust temperature, $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

>>>>

\begin{document}
\title{A Massive Molecular Gas Reservoir in the $z$ = 2.221 Type-2 Active Galactic Nucleus Host Galaxy SMM J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm L}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
  of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne) \citep[\eg][]{Lagache05a}.

  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1-3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a}. \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently
the brightest known lensed
SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceivable evidence of AGN activity in this SMG, as well as the identification of a type-2 quasar.

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy.

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I. Riechers).
We used the 3mm receivers with bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
\rarr 2) line was placed in the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
5\farcs77 for the upper sideband image cube. The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over channel width of 145.8 MHz (corresponding to $\sim$407.2 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and 
rms noise of 0.55 mJy beam\pmOne.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
%MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size of 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density of 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne.
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross on each image indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integer; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) (H14). The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: \CO line emission}
We detect \CO line emission toward the background SMG SMM J0939. Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission. Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 541.65 $\pm$ 31.91 km s\pmOne. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the \CO detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$407.2 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. Lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
\citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
probability density function (PDF) of the model parameters. In the code, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter.

@@

We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
values of the best-fit lens model that \citet{Haas14} performed on Keck K-band near-infrared image. For each of
these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
walkers and 6000 steps to identify the best-fit model parameters.
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit0771}
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
show the negative residuals. \label{fig:lens}}
\end{figure}

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm L}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun\ 
and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

@@

The resulting fit is shown in Figure \ref{fig:SED}, the extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement. The 10$\sigma$ detection of the continuum thereby suggests
non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
emission. Besides, the contours of the 104 GHz continuum are
centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument. This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah. At the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.

@@

\subsubsection{SMM J0939+8315} 
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting on the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a single-temperature, modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where $T$ is the rest-frame characteristic cold dust temperature, $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.
